Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
Finishing the p_y notation

\begin{definition}[Intersection graph]\label{def:intersection-graph}
  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ is the relative interior of $\simplex$.
  %(distributions with full support).
\end{definition}
\begin{proposition} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
\end{proposition}
\begin{proof}
  $(\implies)$
  The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g. \bo{cite}).
  This yields a path for the intersection graph.

@@

  \textbf{Constraints:}
    \begin{align}
      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
      \sum_{y=1}^n p^j(y) x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2}
    \end{align}
\end{definition}

@@

\begin{observation} \label{obs:qfp-invariant-lin}
	For any invertible $A \in \reals^{d \times d}$, if $V,\{X^j : j \in [\ell]\}$ is a feasible solution to the quadratic feasibility program, then so is $(VA),\{A^{-1}X^j : j \in [\ell]\}$.
\end{observation}
\begin{proof}
	The halfspace constraints are $(VA)(A^{-1}X^j) \leq B \iff VX^{j} \leq B$.
	The $j^{th}$ vertex constraint is a vector equality $\sum_{y \in \Y} p^j(y) (A^{-1}X^j)_y = \vec{0}$.
	If we let $a_m$ be the $m^{th}$ row of $A^{-1}$, then the $m^{th}$ row of the vector equality is
	\begin{align*}
	0 &= \sum_{y \in \Y} p^j(y) \inprod{a_m}{x^j_y}  \\
	&= \inprod{a_m}{\sum_{y \in \Y} p^j(y) x^j_y}  \\
	&= 0
	\end{align*}
	so the program is feasible.
\end{proof}

>>>>

\begin{definition}[Intersection graph]\label{def:intersection-graph}
  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ is the relative interior of $\simplex$.
  %(distributions with full support).
\end{definition}
\begin{proposition} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
\end{proposition}
\begin{proof}
  $(\implies)$
  The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\cite{lambert2009eliciting}).
  This yields a path for the intersection graph.

@@

  \textbf{Constraints:}
    \begin{align}
      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
      \sum_{y=1}^n p^j_y x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2}
    \end{align}
\end{definition}

@@

\begin{observation} \label{obs:qfp-invariant-lin}
	For any invertible $A \in \reals^{d \times d}$, if $V,\{X^j : j \in [\ell]\}$ is a feasible solution to the quadratic feasibility program, then so is $(VA),\{A^{-1}X^j : j \in [\ell]\}$.
\end{observation}
\begin{proof}
	The halfspace constraints are $(VA)(A^{-1}X^j) \leq B \iff VX^{j} \leq B$.
	The $j^{th}$ vertex constraint is a vector equality $\sum_{y \in \Y} p^j_y (A^{-1}X^j)_y = \vec{0}$.
	If we let $a_m$ be the $m^{th}$ row of $A^{-1}$, then the $m^{th}$ row of the vector equality is
	\begin{align*}
	0 &= \sum_{y \in \Y} p^j_y \inprod{a_m}{x^j_y}  \\
	&= \inprod{a_m}{\sum_{y \in \Y} p^j_y x^j_y}  \\
	&= 0
	\end{align*}
	so the program is feasible.
\end{proof}
